---
title: "R Notebook"
output: html_notebook
---

```{r}
cars <- read.csv("mode_of_transport.csv")
View(cars)
```

# Structure of the data

```{r}
str(cars)
```
Variables like Engineer, MBA, license contains category values. So, we need to convert them into factors.

```{r}
cars$Engineer = as.factor(cars$Engineer)
cars$MBA = as.factor(cars$MBA)
cars$license = as.factor(cars$license)
cars$Gender = as.factor(cars$Gender)
cars$Transport = as.factor(cars$Transport)
```

# Summary of dataset

```{r}
summary(cars)
```
Here, the minimum age is 18, maximum age is 43 and average age is 27.
We conclude that the majority is of males of approximately 70-77%.
Here, there are more Engineers than MBA's.
And, the most common mode of transport is public transportation.

# Visual Analysis of data



```{r}
boxplot(cars$Age ~ cars$Engineer, main="Engineer's Age")
```
```{r}
boxplot(cars$Age ~ cars$MBA, main="MBA's Age")
```
There's no much difference in the age of Engineers and MBA's.

Let's find differences in the average salary for two professions.

```{r}
boxplot(cars$Salary ~ cars$Engineer, main="Engineer's Salary")
```
```{r}
boxplot(cars$Salary ~ cars$MBA, main="MBA's Salary")
```

There's isn't any major difference in the salary.

Let's see the Work Exp column

```{r}
hist(cars$Work.Exp, main="Distribution of Work Experience")
```

This column is right skewed, this is expected as there would be more juniors then seniors in any firm.

```{r}
boxplot(cars$Work.Exp ~ cars$Gender)
```

The box plot shows that there is an equal distribution of male and female with no such difference in work experience.

```{r}
table(cars$license, cars$Transport)
```
The table clearly shows that those who don't have license uses public transport more.

```{r}
boxplot(cars$Salary ~ cars$Transport, main="Mode of transport according to the salary")
```

Plot clearly shows that as the salary increases the number of individuals with private transport also increases.

Let's see if the age and work experience can be usage of private transport increases

```{r}
cor(cars$Age, cars$Work.Exp)
```
```{r}
boxplot(cars$Age ~ cars$Transport, main="Age and Transport")
```
The plot clearly explains that the higher age prefers private transport.

Let's see with the increase in distance would the employees prefer private or public transport.

```{r}
boxplot(cars$Distance ~ cars$Transport, main="Preference of transport according to distance")
```

In this plot the pattern shows that for longer distance private transport is the preference of employees.

Let's see whether female employees prefer private or public transport

```{r}
table(cars$Gender, cars$Transport)
```
From the above data it is visible that more females prefers Public Transport.

Only 40% female uses private transport and only 30% male uses private transport.

# Data Preparations

Let's find if there is any missing values in the data set.
```{r}
anyNA(cars)
```

```{r}
set.seed(1234)
pd = sample(2, nrow(cars), replace=TRUE, prob = c(0.7, 0.3))
carstrain = cars[pd==1,]
carstest = cars[pd==2,]
carstest$Salary = log(carstest$Salary)
carstest$Engineer = as.factor(carstest$Engineer)
carstest$MBA = as.factor(carstest$MBA)
carstest$license = as.factor(carstest$license)
```



There isn't any missing values in this data set.

## Arrange Test Set

```{r}
library(caret)
random <- createDataPartition(cars$Transport, p=0.70, list=FALSE)

train_set = cars[random,]
test_set = cars[-random,]
```

# Model Building

## Naive Bayes

```{r}
library(e1071)
nb_model <- naiveBayes(train_set$Transport ~ ., data = train_set)

nb_model
```
```{r}
nb_predictions <- predict(nb_model, test_set)
table(nb_predictions, test_set$Transport)
```
## Logistic Regression

```{r}
logistic_model <- glm(Transport~., data = train_set, family = binomial(link = "logit"))
test_set$log.pred <- predict(logistic_model, test_set[1:8], type="response")

table(test_set$Transport, test_set$log.pred>0.5)
```

# KNN

```{r}
trControl <- trainControl(method = "cv", number = 10)
fit.knn <- train(Transport ~ ., method = "knn",
                 tuneGrid = expand.grid(k=2:20),
                 trControl=trControl,
                 metric = "Accuracy",
                 preProcess = c("center", "scale"),
                 data = train_set)
fit.knn
```
```{r}
knn_pred_train <- predict(fit.knn, train_set)

table(knn_pred_train, train_set$Transport)
```
```{r}
knn_pred_test <- predict(fit.knn, test_set)
table(knn_pred_test, test_set$Transport)
```
```{r}
predict(fit.knn, carstest)
```
# Conclusion

- Important variables are Age, Work Exp, Distance and License
- Age and Work Exp are highly correlated
- Employees with work exp more than 10 years and above are likely to use private transport
- Employees who must commute for distance greater than 12 are more likely to use private transport
- People with higher salaries greater than 20k are most likely to use private transportation
- With license, we do see that 81% who commute through private transportation have license and 89% commute through public transport
